Books and Babies: An Analysis of the Relationship between Literacy Rate and Fertility Rate in South Asia (2000-2020)

### 2024-04-01 output/paper/paper.qmd
update paper.qmd

---
title: "Analyzing the Relationship between Female Fertility Rate and Female Literacy Rate in South Asia"
author: "Jagpreet Singh"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
date-format: long
bibliography: references.bib
execute: 
  echo: false
format: pdf
fig-pos: "H"
abstract: TBD
---

>>>>

---
title: "Books and Babies: An Analysis of the Relationship between Literacy Rate and Fertility Rate in South Asia (2000-2020)"
author: "Jagpreet Singh"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
date-format: long
bibliography: references.bib
execute: 
  echo: false
format: pdf
fig-pos: "H"
abstract: This paper utilizes data from the World Bank’s Gender Statistics database to examine the relationship between the adult female literacy rate (% of females ages 15 and above) and fertility rate (total births per woman) in South Asia between 2000-2020. The analysis revealed a negative correlation between the two variables, indicating that as the literacy rate increased, the fertility rate decreased. These findings matter as they highlight the importance of investing in female education and empowerment to manage population growth and promote sustainable development. The insights can guide policymakers make decisions on education initiatives and reproductive health programs to further enhance socioeconomic progress in the region.
---
